A Hitchhiker's Guide to Reproducible Research" # replace with something serious

### 2021-02-11 manuscript.Rmd
add part about readme

<!--I am troubled by how we should recomend to learn git-->
We recommend to attend an online lecture or workshop to learn the ins and outs of Git.

@@

@@

<!--Hands on: Add a license-->
```r
usethis::use_cc0_license()
```

>>>>

<!--I am troubled by how we should recommend to learn git-->
We recommend to attend an online lecture or workshop to learn the ins and outs of Git.

@@

One of the greatest benefits of open research is that other people can freely reuse your materials.
To use your materials, they first have to find them and learn how to use them.
Interested users find out about your project via the readme.
The readme is the first thing they see when they visit your Project.
It should explain to them what your project is about and how to reproduce your project.
You could for example include the abstract of your (planned) paper here.

To add a readme to a repository run:

@@

This will create a file with the name `README.Rmd`.
When you knit this file, it in turn creates a `README.md`.
That means you can include R code or plots etc. within the readme.
The `README.md` file will look pleasant in the webbrowser, just like in Figure \@ref(fig:idea-change).

```{r readme-screenshot, include=FALSE}
# unfortunately css selectors won't work for pdf so we'll use png instead
readme <- here::here("images", "readme.png")
webshot2::webshot("https://github.com/aaronpeikert/repro-tutorial/",
                  file = readme,
                  selector = "div#readme", # only select file change
                  zoom = 1)# higher resolution
```

```{r readme, echo=FALSE, fig.cap="A screenshot of how a change tracked in Git is represented by GitHub.  ", out.width='100%'}
knitr::include_graphics(readme)
```

<!--Hands on: Add a license-->
```r
usethis::use_ccby_license()
```
